University of Florida Knowledge Base Acceleration Notebook

### 2013-10-22 paper/kbanotebook2013/content/implementation.tex
Fix some typos, add minor explanations

Our pipeline of processing the corpus consists of a two layer indexing system 
referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
Chunk Files Index Generator will generate indexes of the chunk files 
that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity 
respectively. This two level indexing will eliminate the need to process each and 
every ChunkFile/StreamItem for every entity. The reason for splitting this task 
into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which 
is written in C++ discards non-mentioning chunk files and will stop further 
processing a chunk file as soon as it finds a mention there. Each chunk file can 
contain up to thousands of SIs which can be so time consuming if we were to 
process them in our Java base code.Processing StreamItems on the other hand is 
done in Java with ideas in mind for later on extensibility by adding other Java libraries.

\subsection{Streaming Slot Value Extraction}
\label{sec:ssve}
\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
\vspace*{-.2in}
\end{figure}

>>>>

Our pipeline of processing the corpus consists of a two layer indexing system 
referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
Chunk Files Index Generator will generate indexes of the chunk files 
that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity 
respectively. This two level indexing will eliminate the need to process each and 
every ChunkFile/StreamItem for every entity. The reason for splitting this task 
into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which 
is written in C++ discards non-mentioning chunk files and will stop further 
processing a chunk file as soon as it finds a mention there. Each chunk file can 
contain up to thousands of SIs which can be so time consuming if we were to 
process them in our Java base code. Processing StreamItems on the other hand is 
done in Java with ideas in mind for later on extensibility by adding other Java libraries.

\subsection{Streaming Slot Value Extraction}
\label{sec:ssve}
\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\includegraphics[width=6in]{./images/Pattern-crop.pdf}
% cropped pdf created using $ pdfcrop Pattern.pdf
\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
\vspace*{-.2in}
\end{figure}
